---
title: "AirBnB"
output: html_notebook
---
```{r}

df = read.csv(file="../data/listings_summary_filtered.csv", encoding = "UTF-8")
print(head(df))
```
Structure of the data frame
```{r}
str(df)
```


Analysing the CSV File

```{r}
# See if "read.csv()" outputs a data frame. It should by default
print(is.data.frame(df))

# Get the dimension of the data frame (column and row length)
print(ncol(df))
print(nrow(df))
```


Summary of the data frame (Only reasonable columns)
```{r}
# remove columns for summary that are not good to inspect mainly because they are strings
summary(subset(df, select = -c(id,description,transit,host_id)))
```
```{r}
mean(df$accommodates)
```

Previous summary showed that all "price" variables are from type string because the the attached "$" sign.
Transform all price columns to be numeric:
```{r}
# gsub() function replaces a substring by a regular expression. "[\\$,]" replaces all $-signs and commas. 
df$price = as.numeric(gsub("[\\$,]", "", df$price))
df$weekly_price = as.numeric(gsub("[\\$,]", "", df$weekly_price))
df$monthly_price = as.numeric(gsub("[\\$,]", "", df$monthly_price))
df$cleaning_fee = as.numeric(gsub("[\\$,]", "", df$cleaning_fee))

# remove % sign as well to improve ordering
df$host_response_rate = as.numeric(gsub("[\\%]", "", df$host_response_rate))

cols <- c("price","weekly_price","monthly_price","cleaning_fee")
# see if that worked as intented and see summary. "NA" mean that no price is given
summary(df[cols])
```

A "query" just for experimental reasons.

Get all listings that have an above average review_score_rating and an above average number of number_of_reviews that
have no cleaning_fee:
```{r}
# important to use "na.rm = TRUE" in mean() function and other aggregation functions
info <- subset(df, review_scores_rating  > mean(review_scores_rating, na.rm = TRUE) & number_of_reviews > mean(df$number_of_reviews) & cleaning_fee == 0)
print(info)
```



<h3> Visualize data </h3>


```{r}
# using advanced ggplot to create graphs
library(ggplot2)
# you might need to install this package by running install.packages("sqldf")'
library(sqldf)

res <- sqldf("SELECT COUNT(neighbourhood) AS count,neighbourhood FROM df WHERE neighbourhood != '' GROUP BY neighbourhood ORDER BY count DESC")
print(res)

amount_of_rows <- 10
new <- data.frame(
  neighbourhood = res[1:amount_of_rows,]$neighbourhood,
  count = res[1:amount_of_rows,]$count
)

# build data frame for "Sonstige" group
tmp <- data.frame(
  neighbourhood = "Sonstige",
  count = sum(res[amount_of_rows:nrow(res),]$count)
)
# combine first columns with group "Sonstige"
new <- rbind(new, tmp)

# lock in factor level order
new$neighbourhood <- factor(new$neighbourhood, levels =new$neighbourhood)
print(new)

ggplot(new, aes(x=neighbourhood, y=count, fill=neighbourhood)) +
   ylim(0, max(new$count) + 200) + 
  scale_x_discrete(limits = rev(levels(new$neighbourhood)))+
  geom_bar(stat="identity", width=0.8 ) +
  geom_text(aes(label=count), hjust=-0.3, size=3.5)+
  coord_flip()+
  theme_minimal() + 
  theme(legend.position="none")

```
Wenn ein Inserat ein superhost icon hat, wird es öfter gebucht?

```{r}
res <- sqldf("SELECT COUNT(*) AS anzahl, sum(number_of_reviews) FROM df WHERE host_is_superhost == 't' AND number_of_reviews != ''")

res2 <- sqldf("SELECT COUNT(*) AS anzahl, sum(number_of_reviews) FROM df WHERE host_is_superhost == 'f'  AND number_of_reviews != ''")


paste("Anzahl der Bewertungen pro Listing für Superhosts und Nicht-Superhosts:")
paste("Superhost: ", res$`sum(number_of_reviews)` / res$anzahl, sep="")
paste("Nicht-Superhost: ", res2$`sum(number_of_reviews)` / res2$anzahl, sep="")


res <- sqldf("SELECT COUNT(*) AS anzahl, sum(review_scores_rating) FROM df WHERE host_is_superhost == 't' AND review_scores_rating != ''")

res2 <- sqldf("SELECT COUNT(*) AS anzahl, sum(review_scores_rating) FROM df WHERE host_is_superhost == 'f'  AND review_scores_rating != ''")

paste("Durschnittliche Review-Bewertung für einen Superhosts und Nicht-Superhosts:")
paste("Superhost: ", res$`sum(review_scores_rating)` / res$anzahl, sep="")
paste("Nicht-Superhost: ", res2$`sum(review_scores_rating)` / res2$anzahl, sep="")


res <- sqldf("SELECT COUNT(*) AS anzahl, sum(host_response_rate) FROM df WHERE host_is_superhost == 't' AND host_response_rate != ''")

res2 <- sqldf("SELECT COUNT(*) AS anzahl, sum(host_response_rate) FROM df WHERE host_is_superhost == 'f'  AND host_response_rate != ''")

paste("Durschnittliche Response-Rate für einen Superhosts und Nicht-Superhosts:")
paste("Superhost: ", res$`sum(host_response_rate)` / res$anzahl, sep="")
paste("Nicht-Superhost: ", res2$`sum(host_response_rate)` / res2$anzahl, sep="")

```

Höhe cleaning_fee mit review_scores_cleanliness
```{r}
res <- sqldf("SELECT COUNT(*) AS anzahl, sum(host_response_rate) FROM df WHERE host_is_superhost == 't' AND host_response_rate != ''")
```

1 Zimmer -> AirCondition -> Prize
```{r}
res <- sqldf("SELECT price FROM df WHERE accommodates == 2 AND amenities LIKE '%Air conditioning%' AND price != 6000")

res2 <- sqldf("SELECT price FROM df WHERE accommodates == 2 AND amenities NOT LIKE '%Air conditioning%' AND price != 6000")

paste("Median-Preis für Wohnungen für zwei Personen mit Klimaanlage und ohne:")
paste("Mit AC: ", median(res$price), sep="")
paste("Ohne AC: ", median(res2$price), sep="")

```

